Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-10-12 paper.tex
Figure placement
Rephrase

After suitable generalization, this leads us to the following model
for the \coqe!shiftrows_! operation, depicted in
Figure~\ref{fig:shiftrows}:
%
\coqfrom{Skinny/Base}{shiftrows}
%
which represents the first half of the diffusion layer.
%
%% * Application: mixcolumns
%% ** figure: psi_ >-> ror 1
%
The second half corresponds to a combinational circuit \coqe!psi_!
%
\coqfrom{Skinny/Base}{psi}
%
which exercises the Naperian structure of \coqe!Rows.T! together with
the underlying Boolean algebra. This is followed by a right rotation
of rows. Altogether, this defines the \coqe!mixcolumns_! operation
depicted in Figure~\ref{fig:mixcolumns}
%
\coqfrom{Skinny/Base}{mixcolumns}

\begin{figure}[htp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[draft=false,height=2.8cm]{shiftrows}
    \caption{Shiftrows (from~\citet{beierle:skinny})}
    \label{fig:shiftrows}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[draft=false,height=2.8cm]{mixcolumns}
    \caption{Mixcolumns (from~\citet{beierle:skinny})}
    \label{fig:mixcolumns}
  \end{subfigure}
\end{figure}

@@

At the heart of this layer stands the substitution box \coqe!s8!,
which is just another combinational circuit (Figure~\ref{fig:s8}):
%
\coqfrom{Skinny/Base}{s8}

These building blocks are chained together to form the confusion
layer, \coqe!subcells!:
%
\coqfrom{Skinny/Base}{subcells}

\begin{figure}
  \centering
  \includegraphics[draft=false,height=5cm]{s8}
  \caption{Substitution box S8 (from~\citet{beierle:skinny})}
  \label{fig:s8}
\end{figure}

@@

If we were to adopt \coqe!state! as our actual representation, the
memory usage of the resulting program would quite poor. It would take
at least 128 bytes to store that many bits (assuming that booleans are
stored in the smallest addressable memory size, a byte). This would be
a terrible waste of memory bandwidth and very poor register usage.

>>>>

After suitable generalization, this leads us to the following model
for the \coqe!shiftrows_! operation, depicted in
Figure~\ref{fig:shiftrows}:
%
\coqfrom{Skinny/Base}{shiftrows}
%
which represents the first half of the diffusion layer.
%
%% * Application: mixcolumns
%% ** figure: psi_ >-> ror 1
%
The second half corresponds to a combinational circuit \coqe!psi_!
%
\coqfrom{Skinny/Base}{psi}
%
which exercises the Naperian structure of \coqe!Rows.T! together with
the underlying Boolean algebra. This is followed by a right rotation
of rows. Altogether, this defines the \coqe!mixcolumns_! operation,
depicted in Figure~\ref{fig:mixcolumns}:
%
\coqfrom{Skinny/Base}{mixcolumns}

\begin{figure}[tp]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[draft=false,height=2.8cm]{shiftrows}
    \caption{Shiftrows (from~\citet{beierle:skinny})}
    \label{fig:shiftrows}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[draft=false,height=2.8cm]{mixcolumns}
    \caption{Mixcolumns (from~\citet{beierle:skinny})}
    \label{fig:mixcolumns}
  \end{subfigure}
\end{figure}

@@

At the heart of this layer stands the substitution box \coqe!s8!
(Figure~\ref{fig:s8}), which is just another combinational circuit:
%
\coqfrom{Skinny/Base}{s8}

These building blocks are chained together to form the confusion
layer, \coqe!subcells_!:
%
\coqfrom{Skinny/Base}{subcells}

\begin{figure}
  \centering
  \includegraphics[draft=false,width=.75\textwidth]{s8}
  \caption{Substitution box S8 (from~\citet{beierle:skinny})}
  \label{fig:s8}
\end{figure}

@@

If we were to adopt \coqe!state! as our actual representation, the
memory usage of the resulting program would quite poor. It would take
at least 128 bytes to store that many bits (assuming that booleans are
stored in the smallest addressable memory size, a byte). This would be
a terrible waste of memory bandwidth and register usage.
